### 2023-02-08 article.tex
Rewrote abstract and last paragraph

Here we define paradata as data about the data collection process.
Computer code is the paradata for a computatioal/academic experiment,
allowing the experiment to be reproduced.
However, code is published alongside an academic
paper in a minority of all cases.
As reproducibility is a cornerstone of science,
research code should be published.
Earlier general recommendations about making paradata (more) useful
is tailored to code, using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.

@@

The world of science would be a more open, humble, trustworthy, truthful
and helpful would the code that accompanies a scientific paper
be treated like a first class citizen. As doing so in an exemplary way
is yet to be rewarded, hence it has to be the idealististic scientists
to wage this battle. I feel the truth and science are worth fighting for
and I hope this paper helps others to join.

>>>>

Paradata is data about the data collection process,
that allows use and reuse of data.
Within the context of computational research,
computer code is the paradata of an experiment,
allowing the study to be reproduced.
A recent study recommended how to make paradata (more) useful,
for paradata in general.
This study applies those recommendations to computer code,
using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.

@@

The world of science would be a more open, humble, trustworthy, truthful
and helpful would the code that accompanies a scientific paper
be treated like a first class citizen. 
Doing so, however, is yet to be rewarded
and still both of the two scientists at the start of this paper 
can provide a good rationale for their behavior.
This will change when reward incentives are put into place 
that reward making paradata useful.
For code specifically, in any computational field,
the rewards are even higher, as reproducibility should again be 
a cornerstone in science.
